### 2019-03-16 README.Rmd
Misc cleanup

**citesdb** is a package to conveniently analyze the full CITES shipment-level wildlife trade database, available at <https://trade.cites.org/>. This data consists of over 20 million records of reported shipments of wildlife and wildlife
products subject to oversight under the [Convention on International Trade in Endangered Species of Wild Fauna and Flora](https://www.cites.org)

@@

### Using the Database

>>>>

**citesdb** is a package to conveniently analyze the full CITES shipment-level wildlife trade database, available at <https://trade.cites.org/>. This data consists of over 20 million records of reported shipments of wildlife and wildlife
products subject to oversight under the [Convention on International Trade in Endangered Species of Wild Fauna and Flora](https://www.cites.org).

@@

### Using the database
